Fluent statistical computing interfaces for biological data analysis

### 2020-03-23 Rmd/05-embeddings.Rmd
add stuff from talk

>>>>

 Look up nearest neighbours graph from points that lie in a brushing region.

Highlight the corresponding neighbours using colour or transparency in the linked view.

- The $k$ nearest neighbours graph can be pre-computed quickly, for either $X$, $Y$ or both.
- Instead of using the neighbour indices, we could use the neighbour distances instead.
- Composition of multiple brushes could be used to show where there are matches/mismatches between nearest neighbour graphs.
